Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-05-31 analysis/paper/London_HauloutBehavior.Rmd
rebuild/re-run analysis; change figure names

@@

Sex and age class (non-dependent _young-of-the-year_, sexually immature
_subadults_, and mature _adults_) were estimated at the time of deployment by
various combinations of length, claw growth ridges [@mclaren1958a], and pelage
characteristics. Seals determined to be less than one year were classified as
young-of-the-year. For those bio-loggers deployed on young-of-the-year and
transmitting into the next year, the age class was advanced to subadult on 1
March of the following year -- the assumed anniversary of their birth. Subadults
are those seals likely greater than one year of age but less than four years.
Adults are individuals that are likely older than four years. Table
\@ref(tab:tblDeploy) provides a summary of these deployments and data received
from them.

@@

This manuscript was developed as a reproducible research compendium and was
originally published as a pre-print (https://doi.org/10.1101/2022.04.07.487572).
All data and code are available on GitHub
(https://github.com/noaa-afsc/berchukseals-haulout) and major versions archived
at Zenodo (https://doi.org/10.5281/zenodo.4638221). Original data sources for
telemetry are archived at the United States Animal Telemetry Network, archived
at Movebank, or associated with other published manuscripts (see supplemental
material \@ref(tab:deploymentTable)). Collated and cleaned data products needed
to replicate the analysis along with the results of all model fits are also
available and versioned as an R package on GitHub
(https://github.com/noaa-afsc/berchuksealsHauloutFits) and archived at Zenodo.

>>>>

options(tinytex.verbose = TRUE)

@@

Sex and age class (non-dependent _young-of-the-year_, sexually immature
_subadults_, and mature _adults_) were estimated at the time of deployment by
various combinations of length, claw growth ridges [@mclaren1958a], and pelage
characteristics. Seals determined to be less than one year were classified as
young-of-the-year. For those bio-loggers deployed on young-of-the-year and
transmitting into the next year (6 ribbon seals; 3 spotted seals), the age class
was advanced to subadult on 1 March of the following year -- the assumed
anniversary of their birth. Subadults are those seals likely greater than one
year of age but less than four years. Adults are individuals that are likely
older than four years. Table \@ref(tab:tblDeploy) provides a summary of these
deployments and data received from them.

@@

This manuscript was developed as a reproducible research compendium and was
originally published as a pre-print at bioRxiv (@london2022;
https://doi.org/10.1101/2022.04.07.487572). All data used in the study and code
are available on GitHub (https://github.com/noaa-afsc/berchukseals-haulout) and
major versions archived at Zenodo (https://doi.org/10.5281/zenodo.4638221).
Original data sources for telemetry are archived as part of datasets at
the United States Animal Telemetry Network (https://portal.atn.ioos.us/), archived at Movebank (see
Movebank ID	732321226), or associated
with other published manuscripts (see supplemental material
\@ref(tab:deploymentTable)). Collated and cleaned data products needed to
replicate the analysis along with the results of all model fits are also
available and versioned as an R package on GitHub
(https://github.com/noaa-afsc/berchuksealsHauloutFits) and archived at Zenodo
(https://doi.org/10.5281/zenodo.10056308).
